\section{Conclusion}

For project 1, our team tested client request response time using iterative servers. 
Project 2 tested the same processes using concurrent servers to compare which method performed best to serve a client. 
Before the actual testing of the client servers, we stated that the iterative performs better under a light request load while the concurrent operates better under a heavy request load. 
The printed graphs for the iterative and concurrent tests include both the light and heavy request load. 
Analysis of the light load results suggest the iterative model was faster while under a light request when serving the client. 
The graph for the Iterative model displayed a steadier work progress and showed a decline and decrease after 40 clients. 
The concurrent server under a light load showed there was a decline and decrease after 30 clients. 
This graph shows that iterative performs better when there is a small number of clients as it has the capability to work better and outperforms the concurrent light load. 

After comparing the light load client request, we tested the heavy load and compared the two graphs. 
The iterative server was able to handle the requests very well until there was a decline and decrease in the request after 60 clients, it then picked itself back up and increased the work load past 70 clients. 
The concurrent request was indeed better than the Iterative as it was shown on the graph. The concurrent had a steady increase as more clients were being served but there was no decrease at all during the work for the client. 
the concurrent server was able to demonstrate it could handle heavy requests with little deviation in performance compared to time.

Our team concluded if a request is small, the best method to implement would be an iterative server. 
However, if the request is large, the concurrent server is the better option to ensure optimal performance. 
Our research also shows there is no ``silver bullet'' when building a server. 
One must have many considerations to build a solution that serves requests in a fast and efficient manner.
